---
title: "Assignment Part 2"
output: pdf_document
---
## Introduction

Now in the second portion of the class, we're going to analyze the ToothGrowth data in the R datasets package.

### Dataset(ToothGrowth): The Effect of Vitamin C on Tooth Growth in Guinea Pigs

Description: The response is the length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).

Format:
A data frame with 60 observations on 3 variables.

[,1]   len	 numeric	 Tooth length
[,2]	 supp	 factor	 Supplement type (VC or OJ).
[,3]	 dose	 numeric	 Dose in milligrams.

### Basic Analysis
First let's try to compare tooth lengths vs. the Vitamin C/orange juice dosage. From the figure, we know that Orange Juice seems to perform better at the 0.5mg dosages, but has a similar result to Vitamin C at the 2.0mg dosage.

```{r}
library(datasets)
data(ToothGrowth)
library(lattice)
histogram(~len|supp, data=ToothGrowth)
xyplot(len~dose|supp, data = ToothGrowth)
```
 

### Basic Summary
The len increase as the doseage increase for both orange juice and Vitamin C.
Orange juice has better performance than Vitamin C as the dosage is low.And also a better average performance.
```{r}
meanOJ <- mean(ToothGrowth[ToothGrowth$supp == "OJ",1])
meanOJ
meanVC <- mean(ToothGrowth[ToothGrowth$supp == "VC",1])
meanVC
```

### Hypothesis
Hypothesis 1: Orange juice and Vitamin C has the same performance.
```{r}
t1 <- t.test(len ~ supp, data=ToothGrowth)
t1$statistic
qt(.95,58)
```

Hypothesis 2: Orange juice and Vitanmin C has the same performance when the dosage is low
```{r}
sub <- ToothGrowth[ToothGrowth$dose == .5, ]
t2 <- t.test(len ~ supp, data=sub)
t2$statistic
qt(.95,dim(sub)[1] -2)
```

### Conclusions for 

H1 fails: since `r t1$statistic ` is above `r qt(.95,58)`

H2 fails: since `r t2$statistic ` is above `r qt(.95,18)`
